Not `Won't you be my neighbor?' \\ But `Should you be my neighbor?'

### 2014-10-01 notes_schooling_consensus_12_04_12.tex
trying to be more careful about disjointed networks when calculating correlation length

\begin{center}
{\bf \LARGE{Information Gathering Strategies in Social Networks}}
\vspace{10pt}
\\ Eleanor Brush
\\ January 18, 2013
\end{center}

@@

%\subsection{Individual Optimization }

\subsection{Adaptive Dynamics }
\subsubsection{Equilibria: ESS, NIS, CSS, dimorphic populations}

\begin{enumerate}
\item if only speed is valued, ESS is maximal
\item but if only accuracy is valued, there is no ESS
\item at intermediate levels of tradeoff, the population can become dimorphic at various pairs of strategies
\item scaling with group size
\end{enumerate}

@@

A reasonable definition of an steady state is a situation in which, for a given pair of resident and invader strategies, the probability of the number of invaders increasing by one is equal to the number of invaders decreasing by one so that the population is at a probabilistic steady state.  The probabilities may never be exactly equal.  However, there is a number of invaders such that the probability of increasing by one is greater than the probability of decreasing by one but if the number increases by one the probability of decreasing becomes greater than the probability of increasing so that the number of invaders will go back and forth between these two sizes.  This is our provisional definition of a steady state number of invaders.  For a given level of tradeoff between speed and variance ($\alpha=.5$) and network size ($N=20$) we find this steady state number (Figure \ref{prop_of_invaders}).

>>>>

\begin{center}
{\bf \LARGE{Information Gathering Strategies in Social Networks}}
\vspace{10pt}
\\ Eleanor Brush
\\ December 27, 2012
\end{center}

@@

\subsection{Individual Optimization }

\subsubsection{Adaptive Dynamics }

@@

A reasonable definition of an equilibrium is a situation in which, for a given pair of resident and invader strategies, the probability of the number of invaders increasing by one is equal to the number of invaders decreasing by one so that the population is at a probabilistic steady state.  The probabilities may never be exactly equal.  However, there is a number of invaders such that the probability of increasing by one is greater than the probability of decreasing by one but if the number increases by one the probability of decreasing becomes greater than the probability of increasing so that the number of invaders will go back and forth between these two sizes.  This is our provisional definition of a steady state number of invaders.  For a given level of tradeoff between speed and variance ($\alpha=.5$) and network size ($N=20$) we find this steady state number (Figure \ref{prop_of_invaders}).
